Fig2: Candidate genes

### 2020-04-29 analysis/figure-2.Rmd
now with control in table 1

```{r DEGs}
# summary DEG results from DESeq2
candidateDEGS <- read_csv("../results/suppletable1.csv") %>%
  filter(gene %in% candidategenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, bldg_lay, lay_inc.d3, inc.d3_inc.d9, inc.d9_inc.d17, hatch_n5, n5_n9)
candidateDEGS

## table 1 summary candidate genes
table1 <- left_join(candidateDEGS, parentalcaregenes) %>%
  select(gene, bldg_lay:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1$numDEGs <- rowSums(is.na(table1)) # count NAs to know how many are NS
table1 <- table1 %>% 
  mutate(sig = ifelse(numDEGs == 6, "NS", "DEG")) %>% 
  arrange(sig, gene)  %>%  select(-sig, -numDEGs)
table1[is.na(table1)] <- " " # replace NA with blank space so it's pretty
table1

>>>>

```{r DEGs}
# summary DEG results from DESeq2
candidateDEGS <- read_csv("../results/suppletable1.csv") %>%
  filter(gene %in% candidategenes) %>%
  mutate(posneg = ifelse(lfc >= 0, "+", "-"),
         sex = recode(sex, "female" = "F", "male" = "M" ),
         tissue = recode(tissue, 
                         "hypothalamus" = "H",
                         "pituitary" = "P", "gonad" = "G")) %>%
  mutate(res = paste(sex, tissue, posneg, sep = "")) %>%
  select(gene, res, comparison)  %>%
  group_by(gene,  comparison) %>%
  summarize(res = str_c(res, collapse = " ")) %>%
  pivot_wider(names_from = comparison, values_from = res) %>%
  select(gene, control_bldg, bldg_lay, lay_inc.d3, inc.d3_inc.d9, inc.d9_inc.d17, hatch_n5, n5_n9)
candidateDEGS

## table 1 summary candidate genes
table1 <- left_join(candidateDEGS, parentalcaregenes) %>%
  select(gene, control_bldg:n5_n9, parentalcare, parentalbehavior, NCBI) %>%
  mutate(parentalcare = if_else(is.na(parentalcare), " ", "X"),
         parentalbehavior = if_else(is.na(parentalbehavior), " ", "X")) %>%
  rename("Literature" = "parentalcare", "GO" =  "parentalbehavior")
table1$numDEGs <- rowSums(is.na(table1)) # count NAs to know how many are NS
table1 <- table1 %>% 
  mutate(sig = ifelse(numDEGs == 6, "NS", "DEG")) %>% 
  arrange(sig, gene)  %>%  select(-sig, -numDEGs)
table1[is.na(table1)] <- " " # replace NA with blank space so it's pretty
head(table1)
